---
title: "Week2"
author: "Yalin Yang"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
    toc_depth: '3'
--- 

## Johnson and Johnson Quarterly Earnings (jj)
* US company Johnson and Johnson
* Quarterly earnings
* 84 quarters
* 1st quarter of 1960 to 4th quarter of 1980

```{r}
library(astsa)
data(jj)
plot(jj,type = 'o',main = 'Johnson and Johnson Quarterly Earnings', ylab = 'Earnings',xlab = 'Years')
```

## Pneumonia and influenza deaths in the U.S. (flu)
* Monthly pneumonia and influenza deaths per 10,000
* people
* 11 years
* From 1968 to 1978

```{r}
data("flu")
plot(flu,main = 'Monthly pneumonia and influenza deaths in US', ylab = 'deaths per 10,000 people',xlab = 'Months')

```

## Land-ocean temperature deviations (globtemp)
* Global mean land-ocean temperature deviations
* Deviations from base period 1951-1980 average
* Measured in degrees centigrade
* For the years 1880-2015.
* http://data.giss.nasa.gov/gistemp/graphs/

```{r}
data("globtemp")
plot(globtemp,main = 'Land-ocean temperature deviations', ylab = 'Deviation',xlab = 'Years')
```

## Purely random process

```{r}
my_ts <- ts(rnorm(100))
my_ts
```

```{r}
acf(my_ts)
```
## How to simulate MA processes in R
**That ACF of MA(q) cuts off at lag q**
```{r fig.height=5, fig.width=12}
# Generate noise
noise <-  rnorm(10000)
ma_2 <- NULL

for(i in 3:10000){
  ma_2[i] <- noise[i] + 0.7* noise[i-1] + 0.2 * noise[i-2]
}

moving_average_process <- ma_2[3:10000]

par(mfrow = c(1,2))
plot(ts(moving_average_process))
acf(moving_average_process)
```

